### 2017-04-13 paper/oopsla17-submission/intro2.tex
emph
minor

\mypara{A Data-Driven Approach}
%
In this paper, we introduce \toolname
\footnote{``Numeric Analysis of Type Errors''; any resemblance to persons living or dead is purely coincidental.}
a \emph{data-driven} approach to error
localization based on supervised
learning (see \citealt{Kotsiantis2007-pj} for a survey).
%
\toolname works by analyzing a large corpus
of training data --- pairs of ill-typed
programs and their subsequent fixes ---
to automatically \emph{learn a model}
of where errors are most likely to
be found.
%
Given a new ill-typed program,
\toolname simply executes the model
to generate a list of potential
blame assignments ranked by likelihood.
%
We evaluate \toolname by comparing its
precision against the state-of-the-art
on a set of over 4,500 ill-typed \ocaml
programs drawn from introductory
programming classes.
%
We show that, when restricted to a
\emph{single} prediction, \toolname's data-driven
model is able to correctly predict
the exact sub-expression that should
be changed 74\% of the time,
29 points higher than \ocaml and
18 points higher than the state-of-the-art
\sherrloc tool.
%
Furthermore, \toolname's accuracy surpasses
85\% when we consider the \emph{top two}
locations and reaches 91\% if consider
the \emph{top three}.
%
We achieve these advances by identifying
and then solving three key challenges.

>>>>

\mypara{A Data-Driven Approach}
%
In this paper, we introduce \toolname
\footnote{``Numeric Analysis of Type Errors''; any resemblance to persons living or dead is purely coincidental.}
a \emph{data-driven} approach to error
localization based on supervised
learning (see \citealt{Kotsiantis2007-pj} for a survey).
%
\toolname analyzes a large corpus
of training data --- pairs of ill-typed
programs and their subsequent fixes ---
to automatically \emph{learn a model}
of where errors are most likely to
be found.
%
Given a new ill-typed program,
\toolname simply executes the model
to generate a list of potential
blame assignments ranked by likelihood.
%
We evaluate \toolname by comparing its
precision against the state-of-the-art
on a set of over 4,500 ill-typed \ocaml
programs drawn from introductory
programming classes.
%
We show that, when restricted to a
\emph{single} prediction, \toolname's data-driven
model is able to correctly predict
the exact sub-expression that should
be changed 74\% of the time,
29 points higher than \ocaml and
18 points higher than the state-of-the-art
\sherrloc tool.
%
Furthermore, \toolname's accuracy surpasses
85\% when we consider the top \emph{two}
locations and reaches 91\% if consider
the top \emph{three}.
%
We achieve these advances by identifying
and then solving three key challenges.
